Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-30 inst/paper/main.tex
random walk

@@

@@

\subsection{Power of Eval}

\subsubsection{How much code is executed inside eval}
- measure number of operations inside eval and outside eval.

- this is useful because if analyzers treat eval as a nop, they may
miss X\% of the code.

\subsubsection{Does eval create observable side-effects}
- measure number of reads and writes by eval outside of its ``bubble''.

- Since R is lazy, even reads can cause promise evaluation and hence,
side-effects.

- Look at writes to non-local scopes. Compare with total number of
writes for reference?

- Categorize side-effects between env passed to eval and other envs.

\subsubsection{Does eval do reflection}
\eval can access parent scopes via reflection. Find number of times it
does that and the depth to which it access parent frames.

@@

5(?) examples from real code.

@@

\section{Analysis Results}

\subsubsection{A taxonomy of eval}

\section{Discussion}

\subsection{Comparison with Javascript}

>>>>

\NOTE{Talk about the percentage of code executed in eval}

@@

\mypara{Side-effects.}
XXX026 total number of reads performed by \eval. \NOTE{What is the definition of a read?  An env lookup?}  XXX027 average number of reads.
XXX028 total number of writes performed by \eval. Average number XXX029.

\NOTE{Aviral wrote''measure number of reads and writes by eval outside
  of its bubble'' --- what is the bubble here?}

XXX029 reads to caller environment -- where caller is the caller of \eval.

XXX030 reads to other caller environment -- i.e. envs that are on the call stack.

XXX031 reads to caller environment -- where caller is the caller of \eval.

XXX032 reads to other caller environment -- i.e. envs that are on the call stack.

Categorize side-effects between env passed to eval and other envs:
\begin{itemize}
\item ephemeral -- read to envs that are created during \eval  XXX033
\item local -- reads to env of the function in which the call to \eval
  lexically occurred; XXX034
\item parent -- reads to parent envs of the local one. XXX035
\item call-stack -- reads to envs that are on the call stack but not
  caller. XXX035.
\end{itemize}

\subsection{LEGACY TEXT}

@@

@@

\NOTE{5(?) examples from real code?}

\subsection{LEGACY TEXT}

@@

\section{Comparison with Javascript}
